Designing a Search for the BBC

### 2013-08-24 coursework.tex
Added title page, appendix, etc. and ensured the coursework PDF builds.
Added bibliography and sort of finished the first chapter.

\documentclass{report}

\title{Designing a Search for the BBC}

@@

@@

\section{Introduction}

@@

@@

@@

>>>>

\documentclass[a4paper]{report}

\title{Designing a Search for the BBC}
\author{Ross Fenning}

@@

\maketitle

\tableofcontents

@@

\section{Rationale}

@@

The target audience for the BBC is effectively the entire population of the UK
and amongst those that do make use of BBC services, there is much diversity
of needs, preferences and technical ability. It is clear it is no small
task to design a search-based discovery mechanism of millions of diverse
pieces of content aimed at millions of diverse people.

A suitable approach for tackling real-word problems is \emph{Soft Systems Methodology} (SSM)
\cite{checkland2006learning}, which will allows us to stand back from
an ontological approach of defining what the search system \emph{is} or
\emph{comprises} and instead take an \emph{epistemological} view of search
as a system. With this view, we could consider a system that holistically
transforms members of the public's desires to find online content into
the consumption of that content -- whether those desires are \emph{precise}
(e.g. they want an exact article known by headline they saw earlier or a
particular programme they missed on television) or those desires are
\emph{fuzzy} (e.g. news about a certain topic, any comedy programme, learning
materials about the Industrial Revolution).

Checkland \cite{checkland1990soft} decribed a \emph{Rich Picture} approach to
representing a problem situation early in SSM approaches.
Given the size and complexity of the
search system as a whole, a useful initial step is to create such an informal
representation of what is known about the problem. Figure~\ref{rich-picture}
shows what I know of the audience, search and most BBC online content areas.
Note that not all areas are covered and a strong emphasis is placed on TV
catch-up (e.g. via the iPlayer product). Radio catch-up is not mentioned
as it shares a lot of similarity with television in terms of use and any
differences are out of scope for this design.

@@

\section{Use cases}

@@

\appendix
\chapter{Proposal}

\input{proposal-contents}

\bibliographystyle{cell}
\bibliography{bibtex}
